Assessing MCR Discussion Usefulness using Semantic Similarity

### 2014-07-28 sections/results.tex
fixed some notations
working on cast study

\subsubsection{Removal of automatically generated messages}
In Gerrit, the comments are composed of human-written comments from reviewers and automatically generated messages.
These automatic messages are generated by Gerrit, continuous integration system, and the sanity bot\footnote{It is a bot that automatically checks new proposed changes for trivial sanity issues, such as line endings, copyright notices, and commit messages} to record activities.
\textit{`Upload patch set 1.'}, \textit{`Change has been successfully cherry-picked to the staging branch as ...'}, and \textit{`Sanity review passed'} are some examples of these messages.

Since these messages are generally record keeping,
they are not substantially relevant to the proposed changes and do not directly impact software quality\cite{Mcintosh} and hence are useless by our definition.
In practice, they are not considered in code review.
They are easily determined as useless by our method and would artificially improve our classification performance.

These messages are identified by looking for the most common lines of text.
Regular expression patterns are then constructed to match these messages.
Occurrences of these patterns are then removed from our dataset prior to further preprocessing.

Automatic messages are also often inserted as part of review comments.
They too are removed from our dataset, leaving us with only human-written part.
We also completely ignored comments whose author is \emph{Qt Continuous Integration System} and \emph{Qt Sanity Bot}.

@@

To answer this question, we randomly sampled 318 comments from our data set and manually identified usefulness as described in previous subsection.
Then, we used these comments for both the training and test data set for our approach to determine its effectiveness.
We also determined the effectiveness of our approach using bootstrapping cross validation:
We randomly selected 90\% of 318 comments for training set and used the remaining 10\% for the validation set.
The performance on the 10\% was measured using precision, recall and F-measure as described in Equation \ref{eq:fmeasure}.
This validation was repeated for 300 times to estimate the mean and variance of the performance.

% \dan{What what the effort in person-hours for this?}
% Thai sez:  Average time per comment is 28 seconds.
%            Since we do a lot of other things while training, it gives us a STDEV of 45 seconds.
%            The median, by the way, is just 10 seconds.

@@

From 318 samples, the number of labeled comments were 85, 60, 51, and 122 for 0, 1, 2, and 3 \texttt{YES} votes, respectively.
To estimate similarity and dissimilarity thresholds, we iterated $s_t$, $d_t$, $s'_t$, and $d'_t$ values from every unique similarity and dissimilarity values in our data set.
% \TODO{.......}. 
% \pick{We cannot brute force for every floating number. How did we calculate this?} 
% \dan{I assume Thai used a numerical optimization or root finding routine such as bisection. You iterate until a value is within a given tolerance.}
% Thai sez: answered.

Table \ref{tb:thresholds} shows 5 sets of thresholds that best classify useful and useless comments based on F$_1$ score.
% \pick{I used dummy results. Please change it}
\pick{What we got from this table? What information can we interpret? The threshold is slightly different? Is it good or bad? Please describes.}

\textbf{Model Effectiveness.}
Figure \ref{fig:scatter} shows relationship between comments class and our similarity thresholds.
The green area represents the \emph{useful} classification model $\Theta(c,S_T=0.015529,D_T=2.494944)$, and the red area represents the \emph{useless} model $\Omega(c,S_T=0.087522,D_T=2.265679)$.
This figure also shows an example comment that fall in the different area\pick{Didn't put yet}.

As shown in the figure, most comments falling in green area are useful comments, while very few useless comments fall in this area.
Similarly, most comments in the red area are considered useless.
However, some comments were not determined (in white area).
From the example comment, it shows that these comments discussed on \TODO{insert topic}, but did not contain any word in common.
Some areas of these two models overlap, making results undeterminable.

Table \ref{tb:classify_number} summarizes the number of classification from this results.
Interestingly, 88\% of useless comments classified by our model have \texttt{YES} = 0 and 1 voting scores.
From useful class, a similar proportion is obtained---that most useful comments have \texttt{YES} = 2 and 3 voting scores

\begin{table}[h]
\centering
\small
\caption{Number of comments classified by our approach against ground truth data}
\begin{tabular}{ccccc}
\hline
& \multicolumn{4}{c}{Class from Ground Truth Data} \\ \cline{2-5}
Our&  Useless  & Unclear  & Unclear & Useful \\
Classifications&  (\texttt{YES}=0) & (\texttt{YES}=1) & (\texttt{YES}=2) & (\texttt{YES}=3) \\
\hline \hline
Useless & 69 & 23 & 7 & 6 \\
Useful & 3 & 12 & 24 & 94 \\
Overlap & 1 & 1 & 0 & 1 \\
Undetermined & 12 & 24 & 20 & 21 \\
\hline
\end{tabular}
\label{tb:classify_number}
\end{table}

\begin{table*}[!t]
\caption{An accuracy of similarity and dissimilarity thresholds for useful and useless comment classifications}
\small
\centering
\def\arraystretch{1.2}
\begin{tabular}{ccccccc}
\hline
Prediction Models  & Rank & $s_t$ & $d_t$ & F-measure & Precision & Recall \\ \hline \hline
\multirow{5}{*}{$\Theta(c,S_T=s_t,D_T=d_t)$}
& 1 & 0.015529 & 2.494944 & 0.741 & 0.701 & 0.787 \\ \cline{2-7}
& 2 & 0.015529 & 3.077129 & 0.740 & 0.693 & 0.795 \\ \cline{2-7}
& 3 & 0.016713 & 2.494944 & 0.739 & 0.704 & 0.779 \\ \cline{2-7}
& 4 & 0.015411 & 2.494944 & 0.738 & 0.696 & 0.787 \\ \cline{2-7}
& 5 & 0.015411 & 3.077129 & 0.738 & 0.688 & 0.795
% \\ \cline{2-7}
% & \multicolumn{3}{r}{Average} &  1.00 & 1.00 & 1.00 \\ \cline{2-7}
%& \multicolumn{3}{r}{Min-Max} &   1.00 - 1.00 & 1.00 - 1.00  & 1.00 - 1.00
\\ \hline \hline
\multirow{5}{*}{$\Omega(c,S_T=s_t,D_T=d_t)$}
& 1 & 0.087522 & 2.265679 & 0.725 & 0.648 & 0.824 \\ \cline{2-7}
& 2 & 0.087522 & 2.250422 & 0.722 & 0.642 & 0.824 \\ \cline{2-7}
& 3 & 0.087522 & 2.324771 & 0.720 & 0.663 & 0.788 \\ \cline{2-7}
& 4 & 0.052856 & 2.265679 & 0.719 & 0.645 & 0.812 \\ \cline{2-7}
& 5 & 0.087522 & 2.249675 & 0.718 & 0.636 & 0.824
% \\ \cline{2-7}
%& \multicolumn{3}{r}{Average} &  1.00 & 1.00 & 1.00 \\ \cline{2-7}
%& \multicolumn{3}{r}{Min-Max} &   1.00 - 1.00 & 1.00 - 1.00  & 1.00 - 1.00
\\ \hline
\end{tabular}
\label{tb:thresholds}
\end{table*}

\textbf{Model Robustness.} After we performed cross validation, we obtained the following result:
for useful and useless classifications,
we obtained an average F$_1$ score of 0.693 and 0.681,
with standard deviation of 0.090 and 0.118, respectively.
This indicates that we can use our approach to classify with confident of 69.8\%.
\pick{Precision? Recall?} \thai{This is some confidence interval...}

>>>>

\subsubsection{Removal of automatically generated messages} To consider only reviewers discussion, we ignored all messages that automatically generated.
%In Gerrit, the comment history is composed of human-written comments from reviewers and automatically generated messages.
These automatic messages are generated by Gerrit, continuous integration system, and the sanity bot\footnote{It is a bot that automatically checks new proposed changes for trivial sanity issues, such as line endings, copyright notices, and commit messages} to record activities. For example, \textit{`Upload patch set 1.'}, \textit{`Change has been successfully cherry-picked to the staging branch as ...'}, and \textit{`Sanity review passed'}. In practice, they are not considered in code review  and are not substantially relevant to the proposed changes and do not directly impact software quality\cite{Mcintosh}.

To do so, we first ignore all comments written by bots i.e. \emph{Qt Continuous Integration System} and \emph{Qt Sanity Bot}. Second, we removed message including reviewers comments by finding common patterns frequently occurred using regular expression. This would leave us only human-written comments that will be used in further preprocessing.

%, . and hence are useless by our definition.
%%They are easily determined as useless by our method and would artificially improve our classification performance.
%These messages are identified by looking for the most common lines of text using regular expression.
%%Regular expression patterns are then constructed to match and remove these messages.
%Occurrences of these patterns are then removed from our dataset prior to further preprocessing.
%
%Automatic messages are also often inserted as part of review comments.
%They too are removed from our dataset, leaving us with only human-written part.
%We also completely ignored comments whose author is \emph{Qt Continuous Integration System} and \emph{Qt Sanity Bot}.

@@

\textbf{Approach.} To answer this question, we randomly sampled 318 comments from our data set and manually identified usefulness.
Then, we used these comments for both the training and test data set for our approach to determine its effectiveness.
We also determined the effectiveness of our approach using bootstrapping cross validation.
We randomly selected 90\% of 318 comments for training set and used the remaining 10\% for the validation set.
The performance on the 10\% was measured using precision, recall and F-measure.
This validation was repeated for 300 times to estimate the mean and variance of the performance.

To manually assess comment usefulness, three participants (the first two authors and one student) independently classify comments by giving a question that “Does this comment technically contribute to its change or not?”. Then, the participants gave a vote for \texttt{YES} if the comment is likely to useful and  \texttt{NO}  if the comment is likely to useless. From the voting scores, we regarded that the comments with three  \texttt{YES}  votes are \emph{useful} comments and the comments with no  \texttt{YES}  votes (i.e. three  \texttt{NO}  votes) are \emph{useless} comments. For the comments with one and two YES’ votes, we defined them as unclear comments.
% \dan{What what the effort in person-hours for this?}
% Thai sez:  Average time per comment is 28 seconds.
%            Since we do a lot of other things while training, it gives us a STDEV of 45 seconds.
%            The median, by the way, is just 10 seconds.

@@

From 318 samples, the number of labeled comments were 85, 60, 51, and 122 for 0, 1, 2, and 3 \texttt{YES} votes, respectively.
To determine similarity and dissimilarity thresholds for useful and useless model, we iterated $s_t$ and $d_t$ values from every unique similarity and dissimilarity values in our data set.
Table \ref{tb:thresholds} shows 5 sets of thresholds that best classify useful and useless comments based on F$_1$ score. We selected the first rank of thresholds for the further analysis and applied models, i.e. useful: $\Theta(c,S_T=0.015529,D_T=2.494944)$ and useless: $\Omega(c,S_T=0.087522,D_T=2.265679)$ on the samples.

\textbf{Classification Result:}  We summarizes the number of classification from result described in Table \ref{tb:classify_number}.  We also show the results and relationship between comments class that manually classified and the similarity thresholds in Fig  \ref{fig:scatter}. The green area represents the \emph{useful} classification model and the red area represents the \emph{useless} model. Thus, the comments drawn in the green area are those satisfied condition of useful model and the comments drawn in the red area are those satisfied condition of useless. While, the comments drawn in the white area are those not satisfied any condition (i.e. undetermined). 
%This figure also shows an example comment that fall in the different area\pick{Didn't put yet}.

%%Interpret: comments & model%%%%
As shown in the figure, most comments drawn in green area are useful and very few useless comments drawn in this area. Similarly, most comments in the red area are useless. The unclear comments are drawn in both area. Between these areas, there is an overlap section. This is because the similarity and dissimilarity values between useful and useless are vague. Both models tend to maximize coverage of classification. Thus, it is possible that there is overlap between these two models. However, from the results, there are few comments drawn in this overlap section. This shows that error of our model is low.
For comments that were undetermined (drawn in white area), we investigate characteristics of these comments. The findings are described in our discussion section.
%From the example comment, it shows that these comments discussed on \TODO{insert topic}, but did not contain any word in common.

%%Interpret: comments & similarity values%%%%
The graph also shows that the useful comments have less distance (not higher than 3 approximately) while most of useless comments have zero similarity. However, the unclear comments are still spread out over the graph which we cannot determine relationship between their similarity.
Furthermore, it is interesting that comments can be clearly separated into two major groups: comments with high similarity values and comment with zero similarity. This indicates that the comments  in each group have relationship other than similarity. This led us to investigate insight into these comments to find other properties in our future work.

From Table \ref{tb:classify_number}, Interestingly, 88\% of useless comments classified by our model have \texttt{YES} = 0 and 1 voting scores.
The similar proportion is obtained for useful comments classified by our model i.e. most useful comments have \texttt{YES} = 2 and 3 voting scores.

\begin{table}[h]
\centering
\small
\caption{Number of comments classified by our approach against ground truth data}
\begin{tabular}{ccccc}
\hline
& \multicolumn{4}{c}{Class from Manual Assessment} \\ \cline{2-5}
Our&  Useless  & Unclear  & Unclear & Useful \\
Classifications&  (\texttt{YES}=0) & (\texttt{YES}=1) & (\texttt{YES}=2) & (\texttt{YES}=3) \\
\hline \hline
Useless & 69 & 23 & 7 & 6 \\
Useful & 3 & 12 & 24 & 94 \\
Overlap & 1 & 1 & 0 & 1 \\
Undetermined & 12 & 24 & 20 & 21 \\
\hline
\end{tabular}
\label{tb:classify_number}
\end{table}

\begin{table*}[!t]
\caption{An accuracy of similarity and dissimilarity thresholds for useful and useless comment classifications}
\small
\centering
\def\arraystretch{1.2}
\begin{tabular}{ccccccc}
\hline
Prediction Models  & Rank & $s_t$ & $d_t$ & F-measure & Precision & Recall \\ \hline \hline
\multirow{5}{*}{\textbf{useful}: $\Theta(c,S_T=s_t,D_T=d_t)$}
& 1 & 0.015529 & 2.494944 & 0.741 & 0.701 & 0.787 \\ \cline{2-7}
& 2 & 0.015529 & 3.077129 & 0.740 & 0.693 & 0.795 \\ \cline{2-7}
& 3 & 0.016713 & 2.494944 & 0.739 & 0.704 & 0.779 \\ \cline{2-7}
& 4 & 0.015411 & 2.494944 & 0.738 & 0.696 & 0.787 \\ \cline{2-7}
& 5 & 0.015411 & 3.077129 & 0.738 & 0.688 & 0.795
% \\ \cline{2-7}
% & \multicolumn{3}{r}{Average} &  1.00 & 1.00 & 1.00 \\ \cline{2-7}
%& \multicolumn{3}{r}{Min-Max} &   1.00 - 1.00 & 1.00 - 1.00  & 1.00 - 1.00
\\ \hline \hline
\multirow{5}{*}{\textbf{useless}: $\Omega(c,S_T=s_t,D_T=d_t)$}
& 1 & 0.087522 & 2.265679 & 0.725 & 0.648 & 0.824 \\ \cline{2-7}
& 2 & 0.087522 & 2.250422 & 0.722 & 0.642 & 0.824 \\ \cline{2-7}
& 3 & 0.087522 & 2.324771 & 0.720 & 0.663 & 0.788 \\ \cline{2-7}
& 4 & 0.052856 & 2.265679 & 0.719 & 0.645 & 0.812 \\ \cline{2-7}
& 5 & 0.087522 & 2.249675 & 0.718 & 0.636 & 0.824
% \\ \cline{2-7}
%& \multicolumn{3}{r}{Average} &  1.00 & 1.00 & 1.00 \\ \cline{2-7}
%& \multicolumn{3}{r}{Min-Max} &   1.00 - 1.00 & 1.00 - 1.00  & 1.00 - 1.00
\\ \hline
\end{tabular}
\label{tb:thresholds}
\end{table*}

\textbf{Validation} After we performed cross validation, we obtained the following result:
for useful and useless classifications,
we obtained an average F$_1$ score of 0.693 and 0.681,
with standard deviation of 0.090 and 0.118, respectively.
This indicates that we can use our approach to classify with confident of 69.8\%.
\pick{Precision? Recall?} \thai{This is some confidence interval...}
